---
name: Michael Mullarkey
position: "Principal Data Scientist"
address: "Lab for Scalable Mental Health"
profilepic: mcmprofessionalshot.jpg
www: mcmullarkey.github.io
email: "mullarkey.mike@gmail.com"
twitter: mcmullarkey
github: mcmullarkey
linkedin: mcmullarkey
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Michael is a clinical psychology PhD with expertise in data science and scaling mental health supports."
output: vitae::twentyseconds
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution,
  "PhD - Clinical Psychology", "2014-2020", "University of Texas at Austin",
  "MA - Clinical Psychology", "2011-2013", "American University",
  "BA - Psychology", "2008-2011", "American University"
) %>% 
  detailed_entries(Degree, Year, Institution)
```

# Work Experience

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year, ~ Institution,
  "Principal Data Scientist", "2020- ", "Lab for Scalable Mental Health",
  "Consulting Data Scientist", "2019- ", "Institute for Mental Health Research",
  "Data Scientist", "2019-2020 ", "Lab for Scalable Mental Health"
) %>% 
  detailed_entries(Position, Year, Institution)
```
# Selected Projects

 * Created an automated screener for suicidality in text data using boosted tree and neural network models that saved 20 hours of "by hand" work per week: [Link to Code on Github](https://github.com/mcmullarkey) 
 
 * Developed a scalable time series forecasting pipeline using tsfresh feature engineering and a random forest algorithm versatile enough to be used across multiple organizations: [Link to Code on Github](https://github.com/mcmullarkey/time_series_prediction_pipeline)
 
 * Designed, engineered, and analyzed multiple nationwide (USA) A/B tests for scalable mental health supports that improved mental health 3 months later in teenagers: [Link to Code on OSF](https://osf.io/uhzdx/)
 
 * Built a Shiny dashboard to track available data for mission-critical projects according to stakeholder identified criteria, used at least once weekly within the organization: [Link to Code on Github](https://github.com/mcmullarkey)
 
 * Gave invited presentations at national conferences on how to create reproducible workflows that resulted in a >90% sign-up rate for reproducible workflow tools: [Link to Presentation Slides](https://osf.io/yjc3u/)

# Skills

 * Expert in R and RStudio (tidyverse, tidymodels, torch, Shiny, R Markdown)
 
 * Familiar with Python (NumPy, Pandas, Scikit-learn, Keras, TensorFlow)
 
 * Familiar with SQL
 
 * Git and Github
 
 * Time Series Forecasting
 
 * Multivariate Data Analysis

# Other Information

 * I have published [>20 technical papers, cited nearly 1,000 times](https://scholar.google.com/citations?user=ncGnGSEAAAAJ&hl=en)
 
 * I have written two [open source](https://osf.io/hzs9m/) mental health [treatment manuals](https://osf.io/2v8k3/) that have been downloaded >1,500 times (including a Dutch translation)
 
 * I co-wrote a [mental health workbook for teens](https://www.amazon.com/Growth-Mindset-Workbook-Teens-Challenges/dp/1684035570/ref=zg_bsnr_171183_1?_encoding=UTF8&psc=1&refRID=ZY6MTMP3FJFAFB3EXDC6) that debuted as the #1 new release in the teen/young adult mental health category on Amazon
 
 * I stream live data science on [Twitch](https://www.twitch.tv/mcmullarkey)
 
 * I created this resume using the vitae package in R, and my code is available [here](https://github.com/mcmullarkey/resume)
 
 * My cat Boo helps me code because [her code review respects piping](https://twitter.com/mcmullarkey/status/1355598013390090246)

