---
name: Michael Mullarkey
position: "Principal Data Scientist"
address: "Lab for Scalable Mental Health"
profilepic: mcmprofessionalshot.jpg
www: mcmullarkey.github.io
email: "mullarkey.mike@gmail.com"
twitter: mcmullarkey
github: mcmullarkey
linkedin: mcmullarkey
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Michael is a clinical psychology PhD with expertise in data science and scaling mental health supports."
output: vitae::twentyseconds
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution,
  "PhD - Clinical Psychology", "2014-2020", "University of Texas at Austin",
  "MA - Clinical Psychology", "2011-2013", "American University",
  "BA - Psychology", "2008-2011", "American University"
) %>% 
  detailed_entries(Degree, Year, Institution)
```

# Work Experience

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year, ~ Institution,
  "Principal Data Scientist", "2020-2021", "Lab for Scalable Mental Health",
  "Consulting Data Scientist", "2019-2021", "Institute for Mental Health Research",
  "Data Scientist", "2019-2020 ", "Lab for Scalable Mental Health"
) %>% 
  detailed_entries(Position, Year, Institution)
```
# Selected Projects

 * Created an automated screener for suicidality in text data using tree-based and neural network models that saved 20 hours of "by hand" work per week: [Link to Code on Github](https://twitter.com/mcmullarkey) 
 
 * Developed a scalable time series forecasting pipeline using tsfresh feature engineering and a random forest algorithm versatile enough to be used across multiple organizations: [Link to Code on Github](https://github.com/mcmullarkey)
 
 * Built a Shiny dashboard to track available data for mission-critical projects according to stakeholder identified criteria, used at least once weekly within the organization: [Link to Code on Github](https://github.com/mcmullarkey)
 
 * Gave invited presentations at national conferences on how to create reproducible workflows for clinical scientists that resulted in a >90% signup rate for reproducible workflow tools: [Link to Presentation Slides](https://osf.io/yjc3u/)

# Skills

 * Expert in R and RStudio (tidyverse, tidymodels, torch, shiny, rmarkdown)
 * Familiar with Python (NumPy, Pandas, Scikit-learn, Keras)
 * Familiar with SQL
 * Git and Github
 * Time Series Forecasting
 * Multivariate Data Analysis

# Other Information

 * I've published [>20 technical papers, cited nearly 1,000 times](https://scholar.google.com/citations?user=ncGnGSEAAAAJ&hl=en)
 * I [stream on Twitch doing live data science](https://www.twitch.tv/mcmullarkey)

